Temporal Graph Cube

### 2023-01-28 TemporalGraphCube/TemporalGraphCube_revision.tex
response 1-29

Interestingly\todo{todo}, we can avoid the problem of choosing an ideal $ A_i'' $ by adopting the partial materialization strategy \kw{MinLevel} \cite{zhao2011graph}, which we will discuss in Section~\ref{sec:partial_materialization}.
%
%Let's recall the time complexity of Algorithm~\ref{alg:temp_cuboid_baseline}: $ O(|\Vr|+\sum_{i=l-t_{base}}^{r-t_{base}}|\Sr[i]|+|S|) $, where $ \Vr $ and $ \Sr[i] $ are the node set and snapshot of the inputed temp-multi-network, $ S $ is the summarized snapshot of the inputed temp-multi-network. Our goal is to get the value of time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} with corresponding $ \Gr_i'' $ of each $ A_i'' $ as the inputed temp-multi-network in $ O(1) $ time and then choose the lowest time complexity and the corresponding $ \Gr_i'' $. We can not stand a higher time complexity to compute the time complexity of Algorithm~\ref{alg:temp_cuboid_baseline}, which will make the process of choosing an ideal $ \Gr_i'' $ unworthy compared to choosing a arbitrary $ \Gr_i'' $. In time complexity of Algorithm~\ref{alg:temp_cuboid_baseline}, . For our basic Algorithm~\ref{alg:temp_cuboid_baseline}, if we maintain a prefix array $ pArray $ for each precomputed $ \Gr_i'' $ of $ A_i'' $, in which
%\begin{equation}
%	\label{eqt:pre_array_baseline}
% 	pArray[i]=\sum_{j=1}^{i}|\Sr''[j]|, i \leq t_{end},
%\end{equation}
%$ \Sr''[j] $ is the snapshot at timestamp $ j+t_{base} $ as defined in Definition~\ref{def:snapshot}, we can easily compute the value of accumulation part ($ \sum_{i=l-t_{base}}^{r-t_{base}}|\Sr[i]| $) in the time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} by
%\begin{equation}
%	\label{eqt:pre_array_base_use}
%	pArray[r-t_{base}]-pArray[l-t_{base}-1].
%\end{equation}
%It is easy to update $ pArray $ and $ \Sr''[j] $ according to their definitions when adding new edges at the latest timestamp in each $ \Gr_i'' $ (we will talk about adding new edges into temporal graph cube in Section~\ref{subsec:growing}). As a result, we can compute the value of time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} with different $ \Gr_i'' $ as the inputed temp-multi-network by $ |\Vr_i''|+pArray[r-t_{base}]-pArray[l-t_{base}-1]+|S_i''| $ in $ O(1) $ time. .[not accurate because of $ |S_i''| $]

@@

As a result, the greedy algorithm and its variations are not suitable for view selection problem in temporal graph cube. In this paper, we adopt a much simpler solution to select views to be precomputed, \kw{MinLevel}, which was originally introduced in \cite{zhao2011graph}. The idea of \kw{MinLevel} is simple: users are more willing to query with small number of dimensions, i.e., $ |dim(A)| $ is small in $ Q=(A,[l,r]) $. In \kw{MinLevel}, view $ A $ where $ |dim(A)|=l_0 $ is in the first batch of views to be selected ($ l_0 $ is an empirical value). If all the views with $ l_0 $ dimensions have been selected and the number of selected views or the total size needed for precomputing the selected views has not reach the limit, then we continue to select views with $ l_0+1 $ dimensions until we select enough number or size of views. In this paper, we select $ k $ views to be precomputed and $ l_0=1 $.

Using \kw{MinLevel}, we precompute views with small number of dimensions; and these views also have high similarity of snapshots in their snapshot arrays (as shown in Table~\ref{tab:materialized_view}). In processing temporal cuboid query $ Q=(A',[l,r]) $, if $ A' $ is not precomputed and $ l_0=1 $, only $ A_{base} $ can be used to process the query $ Q $. If $ l_0>1 $ and $ |dim(A')|<l_0 $, then there may be some precomputed views $ \{A_1'',A_2'',...\} $ where $ |dim(A_i'')|=l_0 $ can be used to process $ Q $. In this case, choosing an arbitrary $ A_i'' $ to process $ Q $ is efficient enough because the size of $ A_i'' $ and its index is usually small since $ l_0 $ is a small value.\todo{todo}

@@

\stitle{Exp-1: Performance of the index-based method.} Here we aim to evaluate how much the index-based solution can accelerate the merging operation of snapshots in time ranges while processing temporal cuboid queries, compared to the baseline algorithm (Algorithm~\ref{alg:temp_cuboid_baseline}). As we analyzed before, the average acceleration ratio of the index-based solution can vary if the similarity of snapshots in temp-multi-networks changes. In this experiment, we mainly use \kw{IMDB} dataset, since vertices in \kw{IMDB} dataset have 7 dimensions and $ 2^7 $ views can be obtained. For convenience, we only materialize views in Table~\ref{tab:materialized_view}, among which we only materialize one view containing dimension \kw{Name}, because \kw{Names} of two persons are hardly the same in \kw{IMDB}, and thus \kw{Name} can be approximately regarded as a primary key and having only one view containing dimension \kw{Name} is enough.
\begin{table}[t!]%\vspace*{-0.3cm}
	\scriptsize
	%\small
	\centering
	\caption{Materialized views} \vspace*{-0.2cm} \label{tab:materialized_view}
	\begin{tabular}{c c c}
		\toprule
		\bf No. & Materialized Views & Similarity of Snapshots \cr %\hline %\hline
		\midrule
		1 & \kw{Pro} & 53.48 \cr %\hline
		\midrule
		2 & \kw{Pro}, \kw{Field} & 18.16 \cr %\hline
		\midrule
		3 & \kw{Pro}, \kw{Field}, \kw{Genre} & 6.15 \cr %\hline
		\midrule
		4 & \makecell[c]{\kw{Pro}, \kw{Field}, \kw{Genre},\\\kw{isAdult}}  & 6.07 \cr %\hline
		\midrule
		5 & \makecell[c]{\kw{Pro}, \kw{Field}, \kw{Genre},\\\kw{isAdult}, \kw{Averating}} & 4.70 \cr %\hline
		\midrule
		6 & \makecell[c]{\kw{Pro}, \kw{Field}, \kw{Genre},\\\kw{isAdult}, \kw{Averating}, \kw{Hotness}} & 3.97 \cr %\hline
		\midrule
		7 & \makecell[c]{\kw{Name}, \kw{Pro}, \kw{Field}, \kw{Genre},\\\kw{isAdult}, \kw{Averating}, \kw{Hotness}} & 1.12 \cr %\hline
		\bottomrule
	\end{tabular}
	\vspace*{-0.4cm}
\end{table}

@@

@@

\begin{figure}[t!]
	\begin{center}
		\begin{tabular}[t]{c}\hspace*{-0.3cm}
		%	\subfigure[{\scriptsize Prefix Array}]{
%				\includegraphics[width=0.25\textwidth]{fig/exp/index_update/index_update_single_a.pdf}
%			}
%			\hspace*{-0.3cm}
%			\subfigure[{\scriptsize STable}]{
%				\includegraphics[width=0.25\textwidth]{fig/exp/index_update/index_update_single_b.pdf}
%			}
%			\hspace*{-0.3cm}
%			%\vspace*{-0.3cm}\\\hspace*{-0.3cm}
			\subfigure[{\scriptsize Time consumption}]{
				\includegraphics[width=0.23\textwidth]{fig/exp/index_update/index_update_single_c.pdf}
			}
	%		\\
%			\hspace*{-0.3cm}
%			\subfigure[{\scriptsize Prefix Array}]{
%				\includegraphics[width=0.25\textwidth]{fig/exp/index_update/index_update_single_d.pdf}
%			}
%			\hspace*{-0.3cm}
%			\subfigure[{\scriptsize STable}]{
%				\includegraphics[width=0.25\textwidth]{fig/exp/index_update/index_update_single_e.pdf}
%			}
			\hspace*{-0.3cm}
			\subfigure[{\scriptsize Space usage}]{
				\includegraphics[width=0.23\textwidth]{fig/exp/index_update/index_update_single_f.pdf}
			}
		\end{tabular}
	\end{center}
	\vspace*{-0.5cm}
	\caption{The updating performance of the index-based solution}
	\vspace*{-0.4cm}
	\label{fig:index_update}
\end{figure}

@@

Our work is also related to graph summarization and analysis. For static graphs, there are some representative works, including graph compression with MDL (Minimum Description Length) principle \cite{navlakha2008graph}, attributed graph compression \cite{wu2014graph} and graph clustering based on vertices partitioning \cite{zhou2009graph}. Recently, there exist several studies on static graph summarization, such as summarizing directed acyclic graph (DAG) \cite{zhu2020top}, summarizing multi-relation graph \cite{ke2022multi} where multiple edges of different types may exist between any pair of vertices, and DPGS model \cite{zhou2021dpgs}, which can preserve properties like graph spectrum and the authorities and hubnesses of vertices while reconstructing graph. \revision{However, all of them ignore the temporal information of big graph data}. For temporal graph and dynamic graph, TimeCrunch \cite{shah2015timecrunch} summarizes a large dynamic graph with a set of important temporal structures using MDL, such as ranged full clique, periodic bipartite core, oneshot star, etc. \revision{Some works (\cite{mudannayake2021kmatrix,tang2016graph,ma2021parameter,ashrafi2021gs4,gou2019fast,chen2022scube}) summarize graph stream into one sketche. \cite{fernandes2018dynamic,tsalouchidou2018scalable} use a sliding window of fixed length to only summarize the latest snapshots, and \cite{ko2020incremental} only summarize the current snapshot of a graph stream incrementally and losslessly}. However, in this paper, we can specify arbitrary time window to query summarized result in real time. \revision{Chen et al. \cite{chen2022horae} also studies summarizing snapshots in arbitrary time window, but they ignored the attributes of vertices and different views determined by combinations of those attributes}. We summarize graphs based on selected attributes of vertices, \revision{so we can get summarized information between vertices in different resolutions.}

\section{Conclusion} \label{sec:conclusion}
In this paper, we extend data warehouse and OLAP technology to temporal multidimensional networks by proposing a new data warehouse model \kw{Temporal\enspace Graph\enspace Cube}, which provides knowledge workers with tools to analyze temporal multidimensional networks. We first extend the basic concepts in static graph cube and introduce two new queries, \kw{temporal\enspace cuboid} and \kw{temporal\enspace crossboid}, allowing \kw{Temporal\enspace Graph\enspace Cube} to support OLAP queries on temporal multidimensional networks. Then, we propose a segment-tree based index method to accelerate the OLAP queries. We also present a new metric to measure the efficiency of the index. We conduct extensive experiments on two large real-world datasets, and the results demonstrate the effectiveness and efficiency of the proposed solutions.

>>>>

As a result, in this paper we choose an arbitrary $ A_i'' $ with least $ |dim(A_i'')| $ in those precomputed views.
%
%Let's recall the time complexity of Algorithm~\ref{alg:temp_cuboid_baseline}: $ O(|\Vr|+\sum_{i=l-t_{base}}^{r-t_{base}}|\Sr[i]|+|S|) $, where $ \Vr $ and $ \Sr[i] $ are the node set and snapshot of the inputed temp-multi-network, $ S $ is the summarized snapshot of the inputed temp-multi-network. Our goal is to get the value of time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} with corresponding $ \Gr_i'' $ of each $ A_i'' $ as the inputed temp-multi-network in $ O(1) $ time and then choose the lowest time complexity and the corresponding $ \Gr_i'' $. We can not stand a higher time complexity to compute the time complexity of Algorithm~\ref{alg:temp_cuboid_baseline}, which will make the process of choosing an ideal $ \Gr_i'' $ unworthy compared to choosing a arbitrary $ \Gr_i'' $. In time complexity of Algorithm~\ref{alg:temp_cuboid_baseline}, . For our basic Algorithm~\ref{alg:temp_cuboid_baseline}, if we maintain a prefix array $ pArray $ for each precomputed $ \Gr_i'' $ of $ A_i'' $, in which
%\begin{equation}
%	\label{eqt:pre_array_baseline}
% 	pArray[i]=\sum_{j=1}^{i}|\Sr''[j]|, i \leq t_{end},
%\end{equation}
%$ \Sr''[j] $ is the snapshot at timestamp $ j+t_{base} $ as defined in Definition~\ref{def:snapshot}, we can easily compute the value of accumulation part ($ \sum_{i=l-t_{base}}^{r-t_{base}}|\Sr[i]| $) in the time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} by
%\begin{equation}
%	\label{eqt:pre_array_base_use}
%	pArray[r-t_{base}]-pArray[l-t_{base}-1].
%\end{equation}
%It is easy to update $ pArray $ and $ \Sr''[j] $ according to their definitions when adding new edges at the latest timestamp in each $ \Gr_i'' $ (we will talk about adding new edges into temporal graph cube in Section~\ref{subsec:growing}). As a result, we can compute the value of time complexity of Algorithm~\ref{alg:temp_cuboid_baseline} with different $ \Gr_i'' $ as the inputed temp-multi-network by $ |\Vr_i''|+pArray[r-t_{base}]-pArray[l-t_{base}-1]+|S_i''| $ in $ O(1) $ time. .[not accurate because of $ |S_i''| $]

@@

As a result, the greedy algorithm and its variations are not suitable for view selection problem in temporal graph cube. In this paper, we adopt a much simpler solution to select views to be precomputed, \kw{MinLevel}, which was originally introduced in \cite{zhao2011graph}. The idea of \kw{MinLevel} is simple: users are more willing to query with small number of dimensions, i.e., $ |dim(A)| $ is small in $ Q=(A,[l,r]) $. In \kw{MinLevel}, view $ A $ where $ |dim(A)|=l_0 $ is in the first batch of views to be selected ($ l_0 $ is an empirical value). If all the views with $ l_0 $ dimensions have been selected and the number of selected views or the total size needed for precomputing the selected views has not reach the limit, then we continue to select views with $ l_0+1 $ dimensions until we select enough number or size of views. In this paper, we select $ k $ views to be precomputed and $k$ is also an empirical value.

\comment{Using \kw{MinLevel}, we precompute views with small number of dimensions; and these views also have high similarity of snapshots in their snapshot arrays (as shown in Table~\ref{tab:materialized_view}). In processing temporal cuboid query $ Q=(A',[l,r]) $, if $ A' $ is not precomputed and $ l_0=1 $, only $ A_{base} $ can be used to process the query $ Q $. If $ l_0>1 $ and $ |dim(A')|<l_0 $, then there may be some precomputed views $ \{A_1'',A_2'',...\} $ where $ |dim(A_i'')|=l_0 $ can be used to process $ Q $. In this case, choosing an arbitrary $ A_i'' $ to process $ Q $ is efficient enough because the size of $ A_i'' $ and its index is usually small since $ l_0 $ is a small value.}

@@

\stitle{Exp-1: Performance of the index-based method.} Here we aim to evaluate how much the index-based solution can accelerate the merging operation of snapshots in time ranges while processing temporal cuboid queries, compared to the baseline algorithm (Algorithm~\ref{alg:temp_cuboid_baseline}). \revision{We will also compare other types of indexes with STree used in this paper later, such as prefix array and sparse table}. As we analyzed before, the average acceleration ratio of the index-based solution can vary if the similarity of snapshots in temp-multi-networks changes. In this experiment, we mainly use \kw{IMDB} dataset, since vertices in \kw{IMDB} dataset have 7 dimensions and $ 2^7 $ views can be obtained. For convenience, we only materialize views in Table~\ref{tab:materialized_view}, among which we only materialize one view containing dimension \kw{Name}, because \kw{Names} of two persons are hardly the same in \kw{IMDB}, and thus \kw{Name} can be approximately regarded as a primary key and having only one view containing dimension \kw{Name} is enough.
\begin{table}[t!]%\vspace*{-0.3cm}
	\scriptsize
	%\small
	\centering
	\caption{Materialized views} \vspace*{-0.2cm} \label{tab:materialized_view}
	\begin{tabular}{c c c}
		\toprule
		\bf No. & Materialized Views & Similarity of Snapshots \cr %\hline %\hline
		\midrule
		1 & \kw{Pro} & 53.48 \cr %\hline
		\midrule
		2 & \kw{Pro}, \kw{Field} & 18.16 \cr %\hline
		\midrule
		3 & \kw{Pro}, \kw{Field}, \kw{Genre} & 6.15 \cr %\hline
		\midrule
		4 & \makecell[c]{\kw{Pro}, \kw{Field}, \kw{Genre},\\\kw{isAdult}}  & 6.07 \cr %\hline
		\midrule
		5 & \makecell[c]{\kw{Pro}, \kw{Field}, \kw{Genre},\\\kw{isAdult}, \kw{Averating}} & 4.70 \cr %\hline
		\midrule
		6 & \makecell[c]{\kw{Pro}, \kw{Field}, \kw{Genre},\\\kw{isAdult}, \kw{Averating}, \kw{Hotness}} & 3.97 \cr %\hline
		\midrule
		7 & \makecell[c]{\kw{Name}, \kw{Pro}, \kw{Field}, \kw{Genre},\\\kw{isAdult}, \kw{Averating}, \kw{Hotness}} & 1.12 \cr %\hline
		\bottomrule
	\end{tabular}
	\vspace*{-0.4cm}
\end{table}

@@

\begin{table}[t!]%\vspace*{-0.3cm}
	\scriptsize
	%\small
	\centering
	\caption{\revision{Performance of prefix array and sparse table}} \vspace*{-0.2cm} \label{tab:effi_other_index}
	\begin{tabular}{c c c c c c}
		\toprule
		\makecell[c]{View\\No.}& $ s $ &\makecell[c]{acce-ratio\\preArr} &\makecell[c]{Space ratio\\preArr}&\makecell[c]{acce-ratio\\STable}&\makecell[c]{Space ratio\\STable}\cr %\hline %\hline
		\midrule
		1&53.48&5.37 & 1.51 &12.92 &9.38 \cr
		\midrule
		2&18.16&3.20 & 2.58 &7.87 &14.45 \cr
		\midrule
		3&6.15 &1.76 & 5.76 &5.15 &26.78 \cr
		\midrule
		4&6.07 &1.74 & 5.84 &5.15 &27.04 \cr
		\midrule
		5&4.70 &1.56 & 7.14 &4.84 &31.74 \cr
		\midrule
		6&3.97 &1.45 & 8.33 &4.58 &35.85 \cr
		\midrule
		7&1.12 &0.85 &27.38 &OM & OM \cr
		\bottomrule
	\end{tabular}
	\vspace*{-0.4cm}
\end{table}
\revision{We also implement prefix array (preArr, only supports $ f_e= $ SUM($\ast$)) and sparse table (STable, only supports $ f_e= $ MAX($\ast$) or MIN($\ast$)) to conduct the same queries as a comparison. The results are shown in Table~\ref{tab:effi_other_index}. We can see that the acceleration ratio of prefix array is close to our solution (STree) but with more space consumption in most cases. The performance of prefix array is also influenced by similarity of snapshots, as we analyzed in Section~\ref{sec:effec_of_indexes}. The acceleration ratio of sparse table is much higher than that of prefix array and STree, but consumes much more space. Building sparse table even leads to an out-of-memory on the No. 7 view. Similarly, the performance of sparse table is also influenced by similarity of snapshots. Overall, our index-based method, STree, is the best in these three method considering both acceleration ratio and space consumption ratio.}

@@

\begin{figure}[t!]
	\begin{center}
		\begin{tabular}[t]{c}\hspace*{-0.3cm}
			%	\subfigure[{\scriptsize Prefix Array}]{
				%				\includegraphics[width=0.25\textwidth]{fig/exp/index_update/index_update_single_a.pdf}
				%			}
			%			\hspace*{-0.3cm}
			%			\subfigure[{\scriptsize STable}]{
				%				\includegraphics[width=0.25\textwidth]{fig/exp/index_update/index_update_single_b.pdf}
				%			}
			%			\hspace*{-0.3cm}
			%			%\vspace*{-0.3cm}\\\hspace*{-0.3cm}
			\subfigure[{\scriptsize Time consumption}]{
				\includegraphics[width=0.24\textwidth]{fig/exp/index_update/index_update_single_c.pdf}
			}
			%		\\
			%			\hspace*{-0.3cm}
			%			\subfigure[{\scriptsize Prefix Array}]{
				%				\includegraphics[width=0.25\textwidth]{fig/exp/index_update/index_update_single_d.pdf}
				%			}
			%			\hspace*{-0.3cm}
			%			\subfigure[{\scriptsize STable}]{
				%				\includegraphics[width=0.25\textwidth]{fig/exp/index_update/index_update_single_e.pdf}
				%			}
			\hspace*{-0.3cm}
			\subfigure[{\scriptsize Space usage}]{
				\includegraphics[width=0.23\textwidth]{fig/exp/index_update/index_update_single_f.pdf}
			}
		\end{tabular}
	\end{center}
	\vspace*{-0.5cm}
	\caption{The updating performance of the index-based solution}
	\vspace*{-0.1cm}
	\label{fig:index_update}
\end{figure}

\begin{figure}
	\begin{center}
		\includegraphics[width=0.9\columnwidth]{fig/exp/minlevel/minlevel.pdf}
	\end{center}
	\vspace*{-0.6cm}
	\caption{\revision{Performance of strategies in partial materialization. $ k $ is the number of views to be materialized}}
	\vspace*{-0.4cm}
	\label{fig:minlevel}
\end{figure}
\noindent\revision{\stitle{Exp-3: Performance of \kw{MinLevel} in partial materialization.} In this experiment we also use \kw{IMDB}. The greedy strategy introduced in Section~\ref{sec:partial_materialization} is not suitable for partial materialization in temporal graph cube due to the uncertain time range specified in queries, which we have analyzed in Section~\ref{sec:partial_materialization}. Instead, we choose a random strategy, i.e., selecting $ k $ views to be materialized randomly, as a comparison to \kw{MinLevel}. We use total response time of 40 temporal cuboid queries to evaluate the performance. In these queries, the number of queries in the format of $ ((A_1,...,A_{x}),[l,r]) $ is almost twice as many as the number of queries in the format of $ ((A_1,...,A_{x+1}),[l,r]) $, because users are more willing to query with less dimensions. The results are shown in Figure~\ref{fig:minlevel}. We can see that as $ k $ increases, all of the 4 strategies achieve better performance because more views are materialized. With proper setting of $ l_0 $, e.g., $ l_0=4 $, \kw{MinLevel} achieves the best performance since most of the queries specified by users have no more dimensions than $ 4 $, and these queries are more possible to be accelerated compared to the case when \kw{Random} strategy is used.}

@@

Our work is also related to graph summarization and analysis. For static graphs, there are some representative works, including graph compression with MDL (Minimum Description Length) principle \cite{navlakha2008graph}, attributed graph compression \cite{wu2014graph} and graph clustering based on vertices partitioning \cite{zhou2009graph}. Recently, there exist several studies on static graph summarization, such as summarizing directed acyclic graph (DAG) \cite{zhu2020top}, summarizing multi-relation graph \cite{ke2022multi} where multiple edges of different types may exist between any pair of vertices, and DPGS model \cite{zhou2021dpgs}, which can preserve properties like graph spectrum and the authorities and hubnesses of vertices while reconstructing graph. \revision{However, all of them ignore the temporal information of big graph data}. For temporal graph and dynamic graph, TimeCrunch \cite{shah2015timecrunch} summarizes a large dynamic graph with a set of important temporal structures using MDL, such as ranged full clique, periodic bipartite core, oneshot star, etc. \revision{Some works (\cite{mudannayake2021kmatrix,tang2016graph,ma2021parameter,ashrafi2021gs4,gou2019fast,chen2022scube}) summarize graph stream into one sketche. \cite{fernandes2018dynamic,tsalouchidou2018scalable} use a sliding window of fixed length to only summarize the latest snapshots, and \cite{ko2020incremental} only summarize the current snapshot of a graph stream incrementally and losslessly}. However, in this paper, we can specify arbitrary time window to query summarized result in real time. \revision{Chen et al. \cite{chen2022horae} also study summarizing snapshots in arbitrary time window, but they ignored the attributes of vertices and different views determined by combinations of those attributes}. We summarize graphs based on selected attributes of vertices, \revision{so we can get summarized information between vertices in different resolutions.}

\section{Conclusion} \label{sec:conclusion}
In this paper, we extend data warehouse and OLAP technology to temporal multidimensional networks by proposing a new data warehouse model \kw{Temporal\enspace Graph\enspace Cube}, which provides knowledge workers with tools to analyze temporal multidimensional networks. We first extend the basic concepts in static graph cube and introduce two new queries, \kw{temporal\enspace cuboid} and \kw{temporal\enspace crossboid}, allowing \kw{Temporal\enspace Graph\enspace Cube} to support OLAP queries on temporal multidimensional networks. Then, we propose a segment-tree based index method to accelerate the OLAP queries. We also present a new metric to measure the efficiency of the index. We conduct extensive experiments on two large real-world datasets, and the results demonstrate the effectiveness and efficiency of the proposed solutions. \revision{Besides, there are other types of temporal networks which are not discussed in our work, for example, temporal networks where edges have both start and end timestamps. It is difficult to assign realistic meaning to some possible positional relationships between the interval of a temporal edge and interval specified in a query. Data warehouse and OLAP technology based on these special datasets are waiting for further discussion.}
